---
title: "[My Quarto template]{.pale}"
subtitle: "{{< fa brands github >}} <https://github.com/JoDudding/quarto-template>"
format: 
  html:
    title-block-banner: true
---

## Quarto

[Quarto]{.rev} enables you to weave together [content]{.primary} and [executable code]{.secondary} into a **finished document**. To learn more about Quarto see <https://quarto.org>.

```{r}
#| label: source-setup
#| include: false
source('scripts/_setup.r')
```

Will try publishing to Quarto Pub. User name is [jo-dudding]{.secondary}

`quarto publish quarto-pub`

::: .callout-warning
Did not work as this is not a book or website project.
:::

Code text uses the font [Fira Code](https://fonts.google.com/specimen/Fira+Code).

```{r}
#| label: sample-code
test <- tibble(x = 1:6, label = letters[1:6]) |> 
  mutate(y = x / 100)
```

@fig-example-chart below demonstrates my ggplot2 theme.

```{r}
#| label: fig-example-chart
#| fig-cap: Caption of example chart
#| fig-alt: You can write alt text to help explain the chart.

ggplot(test, aes(x, y, fill = label)) +
  geom_col() +
  scale_x_comma() +
  scale_y_pct() +
  scale_fill_jo_d(6) +
  labs(
    x = 'X axis',
    y = 'Y axis',
    fill = 'Fill',
    title = 'Title',
    subtitle = 'Subtitle',
    caption = 'Caption'
  )
```

```{r}
#| label: fig-example-chart-2
#| fig-cap: Caption of example chart
#| fig-alt: You can write alt text to help explain the chart.

ggplot(test, aes(x, y, colour = y)) +
  geom_point() +
  scale_x_comma() +
  scale_y_pct() +
scale_colour_jo_c(limits = c(0, 0.1), labels = percent_format(accuracy = 0.1)) +
  labs(
    x = 'X axis',
    y = 'Y axis',
    colour = 'Colour',
    title = 'Title',
    subtitle = 'Subtitle',
    caption = 'Caption'
  )
```



## callouts

::: {.callout-note}
Note that there are five types of callouts, including:
`note`, `warning`, `important`, `tip`, and `caution`.
:::

::: {.callout-tip}
## Tip with Title

This is an example of a callout with a title.
:::

::: {.callout-caution collapse="true"}
## Expand To Learn About Collapse

This is an example of a 'folded' caution callout that can be expanded by the user. You can use `collapse="true"` to collapse it by default or `collapse="false"` to make a collapsible callout that is expanded by default.
:::


## fontawesome extension

This extension provides support including free icons provided by [Font Awesome](https://fontawesome.com/).

For more details see <https://github.com/quarto-ext/fontawesome>

[ {{< fa book size=5x >}} ]{.gold}

## bsicons extension

This extension provides support including icons provided by [Bootstrap](https://icons.getbootstrap.com/).

For more details see <https://github.com/shafayetShafee/bsicons>

[ {{< bi stars size=5em >}} ]{.gold}

## Links

### Theming

- [Bootswatch pulse](https://bootswatch.com/pulse/)
- [Quarto html theming](https://quarto.org/docs/output-formats/html-themes.html)
- [Emil slidecraft 101](https://emilhvitfeldt.com/blog.html#category=slidecraft%20101)
- [Customizing Quarto websites](https://ucsb-meds.github.io/customizing-quarto-websites/#/title-slide)

### Quarto

- [Awesome Quarto links](https://github.com/mcanouil/awesome-quarto)

### R

- [R for Data Science](https://r4ds.had.co.nz/)
- [R packages](https://r-pkgs.org/)
- [What They Forgot to Teach You About R](https://rstats.wtf/)
- [Stat 545](https://stat545.com/)

### Blogs / Workshops

- [Posit blog](https://posit.co/blog/)
- [posit::conf(2023)](https://posit.co/blog/talks-and-workshops-from-posit-conf-2023/)
- [Awesome R-Ladies’ Blogs](https://github.com/rladies/awesome-rladies-blogs)
- []()
- []()

### Project ideas

- [Making circular maps](https://thetidytrekker.com/post/making-circular-maps/making-circular-maps)
- [Quakes dashboard](https://github.com/cwickham/quakes)
- [https://nrennie.rbind.io/blog/script-templates-r/](https://nrennie.rbind.io/blog/script-templates-r/)





